Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-21 rates-neurips-21/rates.tex
minor

As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear, the overall rate would have been a fast $O(1/n)$.
While much is known about surrogate regret bounds for important classes of losses, like proper losses\raf{Bob, others} and margin losses\raf{refs}, general results spanning very broad classes of loss functions are sparse.
Lacking such results, authors instead often prove bounds for specific losses from scratch, e.g. \raf{abstain}.

@@

The second shows that $\zeta$ cannot be smaller than a square root for sufficiently ``non-polyhedral'' surrogates, which are smooth and locally strongly convex.
For these losses, therefore, fast surrogate generalization rates will likely still translate to slow rates for the target.
This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
\begin{theorem}[Lower bound for non-polyhedral]
  \label{thm:main-lower}
  Let $L$ be a locally strongly convex surrogate, with locally Lipschitz gradient.
  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
\end{theorem}
\raf{Comments on general implications?}

>>>>

As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear, the overall rate would have been a fast $O(1/n)$.
\raft{Maybe a good place to cite the IEEE rates paper}
While much is known about surrogate regret bounds for important classes of losses, like proper losses\raf{Bob, others} and margin losses\raf{refs}, general results spanning very broad classes of loss functions are sparse.
Lacking such results, authors instead often prove bounds for specific losses from scratch, e.g. \raf{abstain}.

@@

The second shows that $\zeta$ cannot be smaller than a square root for sufficiently ``non-polyhedral'' surrogates, which are smooth and locally strongly convex.
For these losses, therefore, fast surrogate generalization rates will likely still translate to slow rates for the target.
This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
\begin{theorem}[Lower bound for non-polyhedral]
  \label{thm:main-lower}
  Let $L$ be a locally strongly convex surrogate, with locally Lipschitz gradient.
  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
\end{theorem}
\raf{Comments on general implications, e.g. ``optimality'' of polyhedral?}
